Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-13 doc/report/msc-report.tex
doc/report/msc-report.tex: * included Aerodyne nail crate image as table. * change "paper" to "thesis". * corrected table centering. * changed hash map to hash table. * minor change in OLAP section. * removed numbering of some sections.

Organizations measure their operations by considering many variables. When
these variables are placed in a spreadsheet, which organizations are wont to
do, the variables are set on the x and y axes. Each axis represents a logical
grouping of variables. In the example of a log file of visits to a web site
above, country of origin is one such variable. A variable is generally called
a dimension in this paper.

@@

% image of a spreadsheet.
%\includegraphics[width=70mm]{pictars/aerodyne-nails.png}
%\imagecaptionplease{crates of nails exported}

@@

@@

\subsection{OLAP}

OLAP, which is an acronym for Online analytical processing, is an approach to
quickly answer multi-dimensional analytical queries.

@@

A data cube is a conceptual n-dimensional array of values. It aids in
reasoning about dimensions. In the context of this paper, each dimension of
the cube corresponds to an attribute of the data in question and each point
along the dimension's axis is a value of the corresponding attribute. At any
point where the n dimensions intersect, a measure can be found. For example,
if the dimensions are country and nail type, the point in the cube where
country is equal to Sweden and nail type is equal to tack will contain a
measurement of the units of tack nails sold in Sweden.

@@

\subsection{Projections}

@@

\subsection{Slice and dice}

@@

\begin{center}
    \begin{table}[h]
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    \small \bf Row Key & \small \bf Time & \small \bf Column &
    \multicolumn{2}{|c|}{\small \bf Column} \\
     & \small \bf Stamp & \small "contents:" &
    \multicolumn{2}{|c|}{\small "anchor:"} \\
    \hline
     & t9 & & \small "anchor:cnnsi.com" & "CNN" \\
     & t8 & & \small "anchor:my.lok.ca" & "CNN.com" \\
    "com.cnn.www" & t6 & \small "{\textless}html\textgreater..." & & \\
     & t5 & \small "{\textless}html\textgreater..." & & \\
     & t3 & \small "{\textless}html\textgreater..." & & \\
    \hline
    \end{tabular}
    \caption{Example HBase table.}
    \end{table}
\end{center}

\vspace{-24pt}

\noindent The model above can indeed be thought of as a sparse distributed
multidimensional sorted map. In concept, this multidimensional map is identical
to a nested hash map. The dimensions of this multidimensional map is mapped out
on the row key, the column family and the column qualifier, and possibly also of
the version timestamp.

>>>>

Organizations measure their operations by considering many variables. When
these variables are placed in a spreadsheet, which organizations are wont to
do, the variables are set on the x and y axes. Each axis represents a logical
grouping of variables. In the example of a log file of visits to a web site
above, country of origin is one such variable. A variable is generally called
a dimension in this thesis.

@@

\begin{table}[h]
    \begin{center}
        \begin{tabular}{|l|l|l|l|}
        \hline
         & January & February & March \\
        \hline
        Canada & 120 & 140 & 120 \\
        \hline
        Great Britain & 60 & 50 & 50 \\
        \hline
        Germany & 80 & 100 & 110 \\
        \hline
        Sweden & 40 & 30 & 30 \\
        \hline
        \end{tabular}
        \caption{Spreadsheet showing crates of nails exported.}
    \end{center}
\end{table}

\vspace{-12pt}

@@

\chapterquote{Some random quote might be suitable here.}{Per}
\section*{Introduction}

@@

\subsection*{OLAP}

OLAP\footnote{On-Line Analytical Processing} is an approach to quickly answer
multi-dimensional analytical queries.

@@

A data cube is a conceptual n-dimensional array of values. It aids in
reasoning about dimensions. In the context of this thesis, each dimension of
the cube corresponds to an attribute of the data in question and each point
along the dimension's axis is a value of the corresponding attribute. At any
point where the n dimensions intersect, a measure can be found. For example,
if the dimensions are country and nail type, the point in the cube where
country is equal to Sweden and nail type is equal to tack will contain a
measurement of the units of tack nails sold in Sweden.

@@

\subsection*{Projections}

@@

\subsection*{Slice and dice}

@@

\begin{table}[h]
    \begin{center}
        \begin{tabular}{|l|l|l|l|l|}
        \hline
        \small \bf Row Key & \small \bf Time & \small \bf Column &
        \multicolumn{2}{|c|}{\small \bf Column} \\
         & \small \bf Stamp & \small "contents:" &
        \multicolumn{2}{|c|}{\small "anchor:"} \\
        \hline
         & t9 & & \small "anchor:cnnsi.com" & "CNN" \\
         & t8 & & \small "anchor:my.lok.ca" & "CNN.com" \\
        "com.cnn.www" & t6 & \small "{\textless}html\textgreater..." & & \\
         & t5 & \small "{\textless}html\textgreater..." & & \\
         & t3 & \small "{\textless}html\textgreater..." & & \\
        \hline
        \end{tabular}
        \caption{Example HBase table.}
    \end{center}
\end{table}

\vspace{-12pt}

The model above can indeed be thought of as a sparse distributed
multidimensional sorted map. In concept, this multidimensional map is identical
to a nested hash table. The dimensions of this multidimensional map is mapped
out on the row key, the column family and the column qualifier, and possibly
also of the version timestamp.
